\tool

### 2018-04-27 paper/paper.tex
RW updates and added paragraph to methodology about rec review

\section{Related Work}
%TODO: Use related work from whatever conference committee
This project builds on previous work by researchers examining recommendation systems in software engineering.

Previous research has explored different approaches for recommending tools to software users. Gordon and colleagues developed Codepourri, a system that uses \textit{crowdsourcing} to make recommendations for Python code~\cite{Gordon2015Codepourri}. <gamification> <idea gardening> Linton and colleagues implemented organization-wide learning (OWL) by using system logs make recommendations to employees throughout a company~\cite{Linton2000OWL}. Maltzahn and colleagues developed ToolBox, a ``community sensitive help system'' to recommend Unix commands~\cite{Maltzahn1995Toolbox}. Fischer and colleagues found that systems requiring users to explicitly seek help, or passive help systems, are ineffective and active help systems are more useful for increasing tool awareness~\cite{Fischer1984ActiveHelpSystems}.

Prior work has also studied various techniques to see how software developers learn new information. Piorkowski and colleagues applied \textit{information foraging theory} to software engineers to determined how developers seek information~\cite{FlemingReactiveInformationForaging}. Cockburn and Williams studied pair programming and found it was beneficial for increasing knowledge as a result of 84\% of software engineers they surveyed found it helped them learn `` faster and better
because [they were] always working with a partner''~\cite{Cockburn2001PairProgramming}. <collaborative filtering>, Answer Garden helps users discover new tools based on common questions asked by colleagues~\cite{Ackerman1990AnswerGarden}. Our research presents and implements a novel approach for making tool recommendations to software engineers to increase awareness of useful development tools to help them complete programming tasks.

Toolsmiths have developed automated tools to increase tool discovery among software developers. SpyGlass automatically recommends tools to help users navigate code~\cite{Viriyakattiyaporn2010Spyglass}. We developed \tool~to actively suggest useful programming tools and increase awareness for software engineers. Our approach differs from existing recommendation systems in the design and implementation of our tool.

Existing research has also focused on recommendation styles for tools. <Mike>. This research introduces a novel and distinctive recommendation style based on three unique design principles to increase awareness of useful software engineering tools among developers.

@@

@@

Johnson and colleagues discovered one of the primary barriers to static analysis tool usage among software engineers is false positives in the output~\cite{Johnson2013Why}. To prevent unnecessary recommendations from our system, we manually reviewed all instances where \tool~reported a recommendation should be made. After inspecting each repository modification, \tool~determines whether it is an appropriate case to make a recommendation to the developer. For this study, we streamlined this process to send an email for the authors to review if a recommendation was proposed by our system. After the authors reviewed the code changes, if we deemed it was a true positive case we proceeded to use \tool~to post the comment recommending \textsc{Error Prone} to the developer on the pull request or commit. Otherwise, we noted the instance of a false positive in our approach and did not make the recommendation. In situations where one repository code change provided multiple opportunities for a recommendation, the authors examined each of the changes and selected one of the errors reported as fixed to recommend to the developer.

>>>>

\section{Related Work}
%TODO: Use related work from whatever conference committee
This project builds on previous work by researchers studying recommendations in software engineering.

%Learning in SE
Previous research has examined techniques to improve how software engineers learn new information. Cockburn and Williams studied the software engineering practice of \textit{pair programming}, and found that 84\% of participants found the practice to be beneficial for increasing knowledge and helped them learn `` faster and better because [they were] always working with a partner''~\cite{Cockburn2001PairProgramming}.  Gordon and colleagues developed Codepourri, a system that uses \textit{crowdsourcing} to create visual Python tutorials to improve information presented to learners~\cite{Gordon2015Codepourri}. Piorkowski and colleagues applied \textit{information foraging theory} to software engineers to determine how developers debug and propose software engineering tools integrate this process into their workflow~\cite{FlemingReactiveInformationForaging}. This project also seeks to improve software engineer learning, however our approach specifically aims to increase awareness of useful software engineering tools to help developers in their work.

%Other existing approaches
Researchers have also developed approaches to improve recommendations to software engineers. Fischer and colleagues encourage the use of \textit{active help systems} to guide users over passive help systems that require users to explicitly seek help~\cite{Fischer1984ActiveHelpSystems}. Cao and colleagues introduced \textit{idea gardening}, an approach for helping end-user programmers overcome barriers. Linton and colleagues implemented organization-wide learning (OWL) by using system logs make recommendations to employees throughout a company~\cite{Linton2000OWL}. Our work builds on research in this area by introducing a distinctive recommendation approach with three original design principles to make tool suggestions to developers more effective.

%Other existing tools
More specifically, researchers and toolsmiths have developed automated recommender systems to increase awareness of software engineering tools.  Maltzahn and colleagues developed ToolBox, a ``community sensitive help system'' to recommend Unix commands~\cite{Maltzahn1995Toolbox}.  SpyGlass automatically recommends tools to help users navigate code~\cite{Viriyakattiyaporn2010Spyglass}. To improve the effectiveness of automated system-to-user recommendations, we implemented \tool~to evaluate our novel approach based on design principles derived from user-to-user recommendations.

%Other existing evaluations
Existing research has also focused on different recommendation styles for software engineering tools. Murphy-Hill and colleagues outlined existing ways to make recommendations to present and evaluate new algorithms based on collaborative filtering and feature discovery~\cite{Murphy-HillDeveloperFluency}. Winters and colleagues analyzed different styles of tool recommendationsand found that suggestion style impacts tool adoption for software developers~\cite{Mike Winters}. This research introduces a brand new recommendation style and measures the effectiveness of our approach by comparing it to other various styles of recommendations.

@@

\subsubsection{Recommendation Styles}

@@

We manually reviewed each instance where \tool~reported a recommendation to a developer for two reasons. First, we wanted to ensure that only one \textsc{Error Prone} recommendation was made to each project. This avoids biasing our results by minimizing the chance other GitHub users working on the same project discover the tool from a comment made to that repository. Additionally, in some cases one commit or pull request provided multiple opportunities for a recommendation. In this case, the authors examined each instance and selected one of errors reported  to make a recommendation on.

Next, we inspected cases to avoid making uneccesary recommendations to developers. Johnson and colleagues discovered one of the primary barriers of static analysis tool usage for software engineers is false positive output~\cite{Johnson2013Why}. To prevent multple comments on one project and false positives from our system, we modified \tool~to send an email to the researchers with the proposed recommendation. After checking the code changes, we proceeded to use \tool~to post the comment recommending \textsc{Error Prone} to the developer on their pull request or commit if the fix was deemed to be a true positive and the repository had not previously received a recommendation. Otherwise, we noted the instance as a false positive in our implementation and did not make a recommendation.
